Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/propane.tex
small tweaks to sec 4

Policies for (distributed) control planes differ from data plane policies~\cite{x,y,z}. First, they must account for all failures at specification time; there is no controller at runtime, the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through path preferences, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths may be under-specified (e.g., "prefer customer" does not indicate a concrete path). The \sysname compiler treats such under-specifications as constraints on the set of paths and automatically computes valid sets based on topology.
%
To illustrate \sysname in action, we define policies for the two 
examples described in the previous section.
%
The following section describes how we compile such policies to BGP.

@@

\sysname allows the operator to configure the network with the abstraction that he or she has centralized control over routing and uses a set of high-level constraints to describe the different routes traffic may (or may not) take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network, we first express the idea that for routes leading to our customer,
we prefer using \CD{R1} over \CD{R2} (Policy P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define ExitCust = \Exit(R1 \Prefer R2)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}.

@@

\begin{code}
\Define Routing = \{
     PCust \Path ExitCust \Prefer \End(Cust)
     PInt  \Path \End(\In)
     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)
\}
\end{code}
\noindent
Line 2 of this policy 
defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
that connections to the customer through both routers fail,
a backup route (\CD{\End(Cust)}) is defined that admits traffic along
any path (including those through other networks) that ends at the customer.
Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
inside the user's network and the keyword \Out{} represents any location
outside the user's network.
Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
implements (P1), (P3) and (P4) from Figure~\ref{fig:example1}.

@@

%% define NoTransit = {
%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
%% }
%% \end{lstlisting}
\begin{code}
\Define PP = Peer \OR Prov
\Define PPTrans   = \Enter(PP) \AND \Exit(PP)
\Define CustTrans = \Later(Cust) \AND \Later(Prov)
\Define NoTrans   = \{\True \Path \NOT{}PPTrans \AND \NOT{}CustTrans\}
\end{code}
\noindent
The \CD{NoTrans} constraint above ensures that requirements (P2) and (P5) are satisfied. It says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}. Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failure cases.

@@

In our data center,
there are three main concerns:
(1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
(2) local services must not leak outside the datacenter, and
(3) aggregation must be performed on global prefixes to reduce churn
in the network.

@@

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Routing = \{
    PG1 \OR PG2 \Path \Any
    PL1 \OR PL2 \Path \NOT{}\Enter(\Out)
    \True      \Path \Exit(\Out)
\}
\end{code}
\noindent
The first line states that there is no restriction (\Any)
on how traffic must
traverse the network for global prefixes, aside from the default restriction
that traffic must not pass through the user's network and then loop
back on itself. This means traffic for
\CD{PG*} may be sent either from other routers in the datacenter, or
from external ASes. The second line ensures that traffic for local
prefixes never enters the network from an outside location. This constraint
guarantees that the services remain reachable only to locations
internal to the data center.

>>>>

Policies for (distributed) control planes differ from data-plane
policies~\cite{x,y,z} in a few important ways. First, control-plane
policies must account for all failures at specification time; there is
no controller at runtime, so the routers must be configured in advance to handle failures in a compliant manner.
%
In \sysname, we enable such specifications through a notion of {\em path preferences}, with the semantics that a less-preferred path is taken only when a higher-preference path is unavailable in the network.
%
Second, paths in a control-plane policy may be under-specified (e.g.,
"prefer customer" does not indicate a concrete path). The \sysname
compiler treats such under-specifications as constraints on the set of
allowed paths and automatically computes valid sets based on topology.
%

In the rest of this section, we define \sysname policies for the two 
examples described in the previous section, introducing key aspects of
the \sysname language along the way.  The complete syntax of the
language as well as our strategy for compiling \sysname policies to
BGP is defined in the next section.

@@

\sysname allows the operator to configure the network with the
abstraction that he or she has centralized control over routing.
Specifically, the operator simply provides a set of high-level constraints
that describe the 
different routes traffic may (or may not) take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network from the previous section, we first express the idea that for routes leading to our customer,
we prefer using \CD{R1} over \CD{R2} (Policy P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define ExitCust = \Exit(R1 \Prefer R2)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}.

@@

\begin{code}
\Define Routing = \{
     PCust \Path ExitCust \Prefer \End(Cust)
     PInt  \Path \End(\In)
     \True  \Path ExitCust \Prefer \Exit(Peer) \Prefer \Exit(Prov)
\}
\end{code}
\noindent
Line 2 of this policy 
defines the paths that exit our network to customer prefixes---\CD{ExitCust} defines paths through \CD{R1} and \CD{R2}, and in the event
that connections to the customer through both routers fail,
a backup route (\CD{\End(Cust)}) is defined that admits traffic along
any path (including those through other networks) that ends at the customer.
Line 3 states that traffic for internal prefixes must end in our network, and is otherwise unconstrained.  The special keyword \In{} represents any location
inside the user's network and the keyword \Out{} represents any location
outside the user's network.
Line 4 applies to any other traffic, and allows any routes that leave through a peer with a preference for customers over peers over providers. To summarize our progress, the \CD{Routing} policy
implements P1, P3, and P4 from Figure~\ref{fig:example1}.

@@

%% define NoTransit = {
%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
%% }
%% \end{lstlisting}
\begin{code}
\Define PP = Peer \OR Prov
\Define PPTrans   = \Enter(PP) \AND \Exit(PP)
\Define CustTrans = \Later(Cust) \AND \Later(Prov)
\Define NoTrans   = \{\True \Path \NOT{}PPTrans \AND \NOT{}CustTrans\}
\end{code}
\noindent
The \CD{NoTrans} constraint above ensures that requirements P2 and P5 are satisfied. It says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}. Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failure cases.

@@

In our data center,
there are three main concerns:
(1) traffic for the prefix block allocated to each top-of-rack router must be able to reach that router,
(2) local services must not leak outside the data center, and
(3) aggregation must be performed on global prefixes to reduce churn
in the network.

@@

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Routing = \{
    PG1 \OR PG2 \Path \Any
    PL1 \OR PL2 \Path \NOT{}\Enter(\Out)
    \True      \Path \Exit(\Out)
\}
\end{code}
\noindent
The first line states that there is no restriction (\Any)
on how traffic must
traverse the network for global prefixes, aside from the default restriction
that traffic must not pass through the user's network and then loop
back on itself. This means traffic for
\CD{PG*} may be sent either from other routers in the data center, or
from external ASes. The second line ensures that traffic for local
prefixes never enters the network from an outside location. This constraint
guarantees that the services remain reachable only to locations
internal to the data center.
